Artin Group Presentations of Reflection Groups

### 2014-07-17 Paper.tex
added to Section 6

\begin{lem} (Analogue of 4.6) 
Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$. To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$. But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$

@@

\begin{lem}
\label{5.2 analog}
[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
\end{lem}

After Lemma \ref{lem:one_connected_to_k} we have left to check the relations $(R2)$ when both $i$ and $j$ are connected to $k$ and the relations $(R3)$.  Beginning with the relations $(R2)$, and following cases a-f from Corollary 2.3 in Barot and Marsh:

@@

\item
\begin{align*}
t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_k &= \underline{s_ks_hs_k^{-1}}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
&= s_h^{-1}s_k\underline{s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_1}\\
&=  s_h^{-1}s_ks_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_1s_h\\
\end{align*}

\end{enumerate}

>>>>

\begin{lem}\label{lem:op_homomorphism}
Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$. To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$. But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$

@@

In this section we prove our main result:

\begin{thm}\label{thm:main}
Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$.  Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$\todo{we should pick notation for this}.
\end{thm}

Throughout this section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  To help us define an isomorphism from $A_{\Gamma}$ to $A_{\Gamma^{\prime}}$ we define an element $t_i\in A_{\Gamma}$ for each vertex $i\in \Gamma$ by

\begin{displaymath}
t_i = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow} i \rightarrow k \mbox{ in } \Gamma\\
				s_i & \mbox{otherwise}\\
	\end{cases}
\end{displaymath}

In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main}.

\begin{prop}\label{prop:ti_relations}
The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)^{\prime}$ and $(R3)^{\prime}$ associated to $\Gamma^{\prime}$.
\end{prop}

\begin{proof}[Proof of Theorem \ref{thm:main}]
Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$.  This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.  By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.  Define a homomorphism 
$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$

Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.  Suppose that there is an arrow $i\rightarrow k$ in $\Gamma$.  Then there will be an arrow $k\rightarrow i$ in $\Gamma^{op}$ and hence an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^{\prime}$, so we have that

$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$

Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.  In each of these cases we have that

$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(s_i^{-1})) = \Delta(s_i^{-1}) = s_i$$

Thus $\psi\circ\varphi$ is the identity map on $A(\Gamma^{\prime})$.  By a similar argument $\varphi\circ\psi$ is the identity map on $A(\Gamma)$, and hence $A(\Gamma)\cong A(\Gamma^{\prime}))$.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
After Lemma \ref{lem:one_connected_to_k} we have left to check the relations $(R2)$ when both $i$ and $j$ are connected to $k$ and the relations $(R3)$.  Beginning with the relations $(R2)$, and following cases a-f from Corollary 2.3 in Barot and Marsh:

@@

\item
\begin{align*}
& t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
&= s_h\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}s_h^{-1}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2 \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
&= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
&= e\\
\end{align*}

\end{enumerate}
\end{proof}
